Structuring Theories with Implicit Morphisms

### 2018-09-27 implicit.tex
Bands example

@@

>>>>

\begin{example}\label{ex:dg2gimplicit}
Going back to the morphism presented in \autoref{ex:dg2g}, we simply add the keyword \lstinline|implicit| in front, to declare it to be implicit:
\begin{mmtcode}
implicit view DG2G : ?DivisionGroup -> ?Group =
  universe = universe ❙
  div = [a,b] a ∘ (b⁻¹) ❙
  nonEmpty = e ❙
  // axioms ...❙
❚
\end{mmtcode}
\end{example}

@@

\begin{example}
	For our morphism $\cn{DG2G}$ from \autoref{ex:dg2gimplicit}, this means that all symbols declared in the theory $\cn{DivisionGroup}$ (see \autoref{ex:thgroup}) are now visible in the theory $\cn{Group}$ with the definitions provided by $\cn{DG2G}$.
\end{example}
